---
title: "MR Analysis Report"
output: html_document
params:
  exposure_efo: NA
  outcome_efo: NA
  exposure_trait_name: NA
  outcome_trait_name: NA
  exposure_snps_api: NA
  outcome_snps_api: NA
  exposure_filtered_data: NA
  harmonized_data: NA
  mr_results: NA
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(TwoSampleMR)
library(GWASapi)
library(dplyr)
```

## Overview

This report reproduces the analysis performed in the Shiny application, including retrieving SNPs via GWASapi and conducting Mendelian Randomization.

## EFO IDs and Trait Names

- **Exposure EFO**: `r params$exposure_efo`  
- **Exposure Trait Name**: `r params$exposure_trait_name`  
- **Outcome EFO**: `r params$outcome_efo`  
- **Outcome Trait Name**: `r params$outcome_trait_name`

## Retrieved Exposure SNPs via GWASapi

```{r exposure-snps-api}
ex_snps <- params$exposure_snps_api
if(!is.null(ex_snps) && nrow(ex_snps) > 0) {
  head(ex_snps, 10)
} else {
  "No exposure SNPs retrieved or none available."
}
```

## Retrieved Outcome SNPs via GWASapi

```{r outcome-snps-api}
out_snps <- params$outcome_snps_api
if(!is.null(out_snps) && nrow(out_snps) > 0) {
  head(out_snps, 10)
} else {
  "No outcome SNPs retrieved or none available."
}
```

## Filtered Exposure Data

Below are the exposure-associated SNPs after applying the p-value threshold:

```{r filtered-exposure}
exp_filtered <- params$exposure_filtered_data
if(!is.null(exp_filtered) && nrow(exp_filtered) > 0) {
  head(exp_filtered, 10)
} else {
  "No filtered exposure data found."
}
```

## Harmonized Data

```{r harmonized-data}
harm_dat <- params$harmonized_data
if(!is.null(harm_dat) && nrow(harm_dat) > 0) {
  head(harm_dat, 10)
} else {
  "No harmonized data available."
}
```

## MR Results

```{r mr-results}
mr_res <- params$mr_results
if(!is.null(mr_res) && nrow(mr_res) > 0) {
  mr_res
} else {
  "No MR results available."
}
```
