
---
title: "Mendelian Randomization Analysis Report"
output: html_document
params:
  harmonized_data: NULL
  mr_results: NULL
---

# Mendelian Randomization Analysis Report

This report provides the results of the Mendelian Randomization (MR) analysis performed in the Shiny app.

---

## **Harmonized Data**
The harmonized data used for the MR analysis is summarized below.

```{r echo=FALSE}
if (!is.null(params$harmonized_data)) {
  knitr::kable(params$harmonized_data, caption = "Harmonized Data", row.names = FALSE)
} else {
  "No harmonized data available."
}
```

---

## **MR Results**
The results of the Mendelian Randomization analysis are shown below.

```{r echo=FALSE}
if (!is.null(params$mr_results)) {
  knitr::kable(params$mr_results, caption = "MR Results", row.names = FALSE)
} else {
  "No MR results available."
}
```

---

## **Summary**
This report was generated automatically from the Shiny app and includes:
- The harmonized data used for the analysis.
- The results of the Mendelian Randomization analysis.

Generated on: `r Sys.Date()`
```

